Revisiting the Truisms of Software Engineering:\\ Does Phase Delay Dramatically Increases Repair Time?

### 2015-03-04 phaseDelay.tex
Updates from ShareLaTeX

Accordingly, this paper revisits
the {\em phase delay} effect
i.e.  the time required to resolve an issue in a software project increases dramatically 
the longer it remains in the system. 
Phase delay has long been
a    motivator for major changes to
SE practices. Basili \& Boehm comment that since the 1980s,  phase delay:
\begin{quote}
...has been a major driver in focusing
industrial software practice on thorough
requirements analysis and design,
on early verification and validation, and
on up-front prototyping and simulation
to avoid costly downstream fixes~\cite{boehm01}.
\end{quote}
Basili and Boehm are not alone in this assessment of the significance of the phase delay effect.
Previously~\cite{me08a}, we have constructed return-on-investement models
for a common practice amongst U.S. government contractors: 
independent verification \& validation. IVV has been criticised as
ineffective since IVV engineers, who many  unfamiliar with the details of the project, are required to pass judgement on the code.
Hence,  the IVV team may find the same or fewer bugs
as the developers,
On the other hand, IVV has been defended
as follows:  when the IVV team finds bugs earlier that the developers then, due to the phase delay effect, this saves the overall cost of the project. Note that the strength of this argument diminishes
if fixing later-phase issues is not significantly more expensive than fixing them earlier.

@@

\begin{figure*}[!t]
\begin{center}
\includegraphics[width=6in]{waterfall2.png}
\end{center}
\caption{Different approaches to software development:  waterfall and agile (bottom left).}
\end{figure*}

>>>>

Accordingly, this paper revisits
the {\em phase delay} effect
i.e.  the time required to resolve an issue in a software project increases dramatically 
the longer it remains in the system. 
Phase delay has long been
a    motivator for major changes to
SE practices. Basili \& Boehm comment that since the 1980s,  phase delay:
\begin{quote}
...has been a major driver in focusing
industrial software practice on thorough
requirements analysis and design,
on early verification and validation, and
on up-front prototyping and simulation
to avoid costly downstream fixes~\cite{boehm01}.
\end{quote}
Basili and Boehm are not alone in this assessment of the significance of the phase delay effect.
Previously~\cite{me08a}, we have constructed return-on-investement models
for a common practice amongst U.S. government contractors: 
independent verification \& validation. IVV has been criticized as
ineffective since IVV engineers, who many  unfamiliar with the details of the project, are required to pass judgement on the code.
Hence,  the IVV team may find the same or fewer bugs
as the developers,
On the other hand, IVV has been defended
as follows:  when the IVV team finds bugs earlier that the developers then, due to the phase delay effect, this saves the overall cost of the project. Note that the strength of this argument diminishes
if fixing later-phase issues is not significantly more expensive than fixing them earlier.

@@

\begin{figure*}[!t]
\begin{center}
\includegraphics[width=6in]{waterfall3.png}
\end{center}
\caption{Different approaches to software development:  waterfall and agile (bottom left).}
\end{figure*}
